Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-08-29 code/analysis.Rmd
done for tonight

fitdata %>%
  ggplot(aes(x = pump_freq, y = k_t, ymin = k_t - 1.96*dk_t, ymax = k_t + 1.96*dk_t, color = dowel_density)) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 3)) +
  geom_errorbar(width = 3, position = "dodge") +
  scale_color_hue(h.start = 0) +
  theme_minimal()

@@

final %>%
  ggplot(aes(x = pump_freq, y = k_s, ymin = k_s - 1.96*dk_s, ymax = k_s + 1.96*dk_s, color = dowel_density)) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 3)) +
  geom_errorbar(width = 3, position = "dodge") +
  scale_color_hue(h.start = 0) +
  theme_minimal()

@@

final %>%
  filter(dowel_density != "0000") %>%
  ggplot(aes(x = pump_freq, y = k_c, ymin = k_c - 1.96*dk_c, ymax = k_c + 1.96*dk_c, color = dowel_density)) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 3)) +
  geom_errorbar(width = 3, position = "dodge") +
  scale_color_hue(h.start = 0) +
  theme_minimal()
```

@@

final %>%
  filter(dowel_density != "0000") %>%
  ggplot(aes(x = pump_freq, y = eta, ymin = eta - 1.96*deta, ymax = eta + 1.96*deta, color = dowel_density)) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 3)) +
  geom_errorbar(width = 3, position = "dodge") +
  scale_color_hue(h.start = 0) +
  theme_minimal()

>>>>

fitdata %>%
  ggplot(aes(x = pump_freq, y = k_t, ymin = k_t - 1.96*dk_t, ymax = k_t + 1.96*dk_t, color = dowel_density)) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 3)) +
  geom_errorbar(width = 3, position = "dodge") +
  scale_color_manual(values = c("black","blue","green","red")) +
  theme_minimal()

@@

final %>%
  ggplot(aes(x = pump_freq, y = k_s, ymin = k_s - 1.96*dk_s, ymax = k_s + 1.96*dk_s, color = dowel_density)) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 3)) +
  geom_errorbar(width = 3, position = "dodge") +
  scale_color_manual(values = c("black","blue","green","red")) +
  theme_minimal()

@@

final %>%
  filter(dowel_density != "0000") %>%
  ggplot(aes(x = pump_freq, y = k_c, ymin = k_c - 1.96*dk_c, ymax = k_c + 1.96*dk_c, color = dowel_density)) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 3)) +
  geom_errorbar(width = 3, position = "dodge") +
  scale_color_manual(values = c("blue","green","red")) +
  theme_minimal()
```

@@

final %>%
  filter(dowel_density != "0000") %>%
  ggplot(aes(x = pump_freq, y = eta, ymin = eta - 1.96*deta, ymax = eta + 1.96*deta, color = dowel_density)) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 3)) +
  geom_errorbar(width = 3, position = "dodge") +
  scale_color_manual(values = c("blue","green","red")) +
  theme_minimal()
